---
title: "CPSCSKILLCHECK2, GROUP4, geom_map"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("ggplot2")
library("rnaturalearth")
library("sf")
library("rnaturalearthdata")
library("maps")
```

#geom_map

#Example 1: Adding Color to a map

#Start by loading the world map
#TIPS: there are hidden packages sometimes, so if the code isn't working, make sure to check if you have all of the libraries installed

#VERY IMPORATNT: instal PACKAGES FIRST rnaturalearthdata, rnaturalearth, ggplot2, maps

#Create the map!

```{r}

theme_set(theme_bw())

world <-ne_countries(scale = "medium", returnclass = "sf")
class(world)
ggplot(data=world) +
  geom_sf()
```

#Add axis labels, title and subtitle

```{r}
ggplot(data = world) +
    geom_sf() +
    xlab("Longitude") + ylab("Latitude") +
    ggtitle("World map", subtitle = paste0("(", length(unique(world$NAME)), " countries)"))
```
#Adding color to the map

```{r}
ggplot(data = world) +
    geom_sf() +
    xlab("Longitude") + ylab("Latitude") +
    ggtitle("World map", subtitle = paste0("(", length(unique(world$NAME)), " countries)")) +
    geom_sf(color = "yellow", fill = "purple")
```
#EXAMPLE 2: PLOTTING EARTHQUAKES

```{r}
world<-ne_countries(scale="medium", returnclass="sf")
basefiji<-ggplot(data=world)+geom_sf()+xlab("Latitude") +ylab("Longitude")+
  coord_sf(xlim=c(165,180),ylim=c(-35,-10), expand=TRUE)
data("quakes")
basefiji+geom_point(data=quakes,
                    mapping=aes(x=long,y=lat,
                                color=mag),
                    alpha=0.50)
```
#yay! wonderful map!

#EXAMPLE 3: POPULATION

```{r}
world<-ne_countries(scale="medium",returnclass="sf")

basefiji<-ggplot(data=world)+geom_sf()+xlab("latitude")+ylab("Longtitude")+
  ggtitle("Fiji")+ ggtitle("Figi Population")
  coord_sf(xlim=c(165,180),ylim=c(-35,-10),expand=TRUE)

basefiji+geom_sf(aes(fill=pop_est))+scale_fill_viridis_c(option="plasma",
                                                         trans="sqrt")+coord_sf(xlim=c(165,180),ylim=c(-35,-10), expand= TRUE)
```
#Great! Almost there! One more example

#EXAMPLE 4:CITY NAMES
This method uses Longitude and Latitude to locate the different cities within a selected region
Able to take a small section of a large data set (world) and only find the map of a certain country and add city names to to the map. 
Able to use names of the city using world.cities data set
Located in the maps package
Labeled this as names
For city names 
Make sure check_overlap is TRUE 
If not, all the cities will be overlapping each other, making it impossible to read

```{r}

world<-ne_countries(scale="medium",returnclass="sf")

ggplot(data=world)+
  geom_sf()+
  coord_sf(xlim=c(175,180), ylim=c(-20,-12), expand=TRUE)

world<-ne_countries(scale="medium",returnclass="sf")

basefiji<-ggplot(data=world)+geom_sf()+xlab("latitude")+ylab("Longitude")+ggtitle("Figi Cities")+coord_sf(xlim=c(165,180),ylim=c(-35,-10),expand=TRUE)

data("world.cities")
basefiji+geom_text(data=world.cities,
                   mapping=aes(x=long,y=lat,label=name),
                   color="hotpink",frontface="plain",check_overlap=TRUE)
```
