---
title: "skills check 2.1"
author: "cami"
date: "10/5/2021"
output: html_document
---

Before going into graphing, we first have to ask "What is Continuous Data?"
Continuous data is quantitative and can take any value


#Geom_point: What is it and what it does#
-Scatter Plot
-Control point size, shape, color, and fill
-Makes it easy to visualize and chart data within the base we are already using
displaying the relationship between two continuous variables
-Able to add bars and other factor for teachers.

#Start with basics:
A <- ggplot(data)

Choose type of plot wanted
B <-A + C <- geom_point (D)

To add points together add on to equation a second one with + in between the two 
chunk of instructions
E: B <-A + C <- geom_point (D)

To add points together add on to equation a second one with + in between the 
two chunk of instructions

Add “aesthetics” (AES) which allow you to format your graph using x,y, color, 
fill, group, shape, size etc

To add more to the aesthetics of the plot, after “blue” inserts a coma and the 
next command
….= blue, size = 3)

#Working example of geom_point
```{r}
ggplot(chickwts, aes(weight, feed)) + geom_point(colour = "blue")
```
#Geom_line: What it is and What it does
Overall, geom_line () serves as a way to make a line graph
It uses the points provided by geom_point and connects them in order of the 
variable on the x axis.
It also highlights exactly when changes occur in the dataset. 

#parts to incorporate in geom_line
If you want to make a line chart, you need to use geom_line to do it.
The ggplot() function indicates that we're going to plot something
The code data = indicates that we'll be plotting data that's contained within a 
dataframe.

After the data parameter, the aes() function is specifying our variable mappings. 
Specifically, assigning what is the x axis and what is the y axis
Finally, we're using geom_line() to indicate that we want to draw line geoms. 

You can also change the appearance of the lines by specifying the color and type
ex. geom_line(color="blue", linetype=2)

Here are 4 line type variations of the same graph
```{r}
a <- c(1,2,4,5,3)
b <- c(5,4,2,1,7)
qplot( a, b, geom="blank") + geom_point() + geom_line(color="blue", linetype=2)
qplot( a, b, geom="blank") + geom_point() + geom_line(color="blue", linetype=4)
qplot( a, b, geom="blank") + geom_point() + geom_line(color="blue", linetype=3)
qplot( a, b, geom="blank") + geom_point() + geom_line(color="blue", linetype=1)
```
#Let’s Look at a Coded Example:
I used the iris data set because it has continuous data types
We will be plotting the Sepal.Width against Sepal.Length
We also want include a factor to show the species 

Heres an outline of the example:
1. The ggplot() function indicates that we're going to plot something.
2. We put the dataset first in the parenthesis to indicate that we'll be 
plotting data that's contained within the iris dataframe. 
3. After the data parameter, the aes() function is specifying our variable 
mappings. Specifically, what we want the x-axis and y-axis to be 
4. we want to include a factor that shows the species by color. We do this by 
saying "color = species"

I also included geom_point to start the data off as a scatter plot
Finally, We're using geom_line() to indicate that we want to draw line geoms. 


Your code should look like this
```{r setup, include=TRUE}
data("iris")
ggplot(iris, aes( x = Sepal.Length, y = Sepal.Width, color = Species)) + geom_point() + geom_line()
```
As shown, there are 3 separate lines indicated by the species color. The 
geom_points are connected by lines and we are able to see the relationship
between Sepal.Length and Sepal.Width. 

#Geom_qq_line (Quantile to Quantile): What it is & what it does

It computes the slope and intercept of the line connecting the points at 
specified quartiles of the theoretical and sample distributions.
It also helps us determine whether a range of numbers has a certain 
distribution: the closer the data points are to being a straight line, the 
closer the data is to the distribution. 


#Geom_qq_line: How to use
In our example, mtcars is our data
for aesthetics, aes is written as aes (sample = mpg, colour = factor, (cyl))
stat_qq () → produces a quantile-quantile plot
stat_qq_line () → compute slope & intercept connecting the points
overall it should look like this
ggplot (mtcars, aes (sample = mpg, colour = factor(cyl))) + stat_qq () + 
stat_qq_line ()

Here is a working example:
```{r}
ggplot(mtcars, aes(sample = mpg, colour = factor(cyl))) +
  stat_qq() +
  stat_qq_line()
```