---
title: "Group 2"
author: "Gabriella Dauber"
date: "10/5/2021"
output: html_document
group: "Group 2 - Continuous y and Categorical x Data" 
---

# Gabriella Dauber's Section // Bar Plot

# Bar Plot: Method to graphically compare the numbers/frequencies of a category or characteristic with another
#Bars break down categorical data by group

# a) Stacked Bar Plot: The subgroups are displayed on top of each other, not beside. 

# b) Grouped Bar Plot: Displays a numeric value for a set of entities split in groups or subgroups. 

# c) Mean Bar Plot: Displays the average of the numerical data for a set of entities. 

# d) Width Change Within Bar Plot: Allows the user to control the bar width with the function geom_bar(). 

# e) Horizontal Bar Plot: The vertical axis represents the categories being compared and the horizontal axis represents a value. 

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, y=uptake, fill=Treatment)) + geom_bar(stat="identity") + xlab("City") + ylab("Uptake of CO2")

```

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, y=uptake, fill=Treatment)) + geom_bar(position="dodge", stat="identity") + xlab("City") + ylab("Uptake of CO2")

```

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, y=uptake, fill=Treatment)) + geom_bar(position="dodge",stat="summary",fun.y="mean") + xlab("City") + ylab("Uptake of CO2")

```

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, y=uptake, fill=Treatment)) + geom_bar(position="dodge", stat="identity", width=0.4) + xlab("City") + ylab("Uptake of CO2")

```

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, y=uptake, fill=Treatment)) + geom_bar(position="dodge", stat="identity", width=0.4) + xlab("City") + ylab("Uptake of CO2") + coord_flip()

```

# Isabelle DuMontier's Section // Box Plots 

# Box Plots: Method for graphically depicting groups of numerical data through their quartiles
# They also may have lines extending from the boxes indicating variability outside the upper and lower quartiles


```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, y=uptake)) + geom_boxplot() + xlab("City")+ ylab("Uptake of CO2")

```

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=factor(conc), fill=Treatment, y=uptake)) + geom_boxplot() + xlab("Concentration") + ylab("Uptake of CO2") 
```

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, fill=Treatment, y=uptake)) + geom_boxplot() + xlab("City") + ylab("Uptake of CO2")
```

```{r}
data(CO2)
library(ggplot2)
ggplot(CO2, aes(x=Type, fill=Treatment, y=uptake, color=factor(conc))) + geom_boxplot() + xlab("City") + ylab("Uptake of CO2")
```

# Alan Lu's Section // Violin Plots 

# Shows distribution of numeric data for multiple groups using density curves
# Usually these graphs are accompanied by a different chart type, like a box plot

```{r}
library(ggplot2)
ggplot(CO2, aes(x= Type, y= uptake, fill = Treatment)) + geom_violin() + xlab("City") + ylab("Uptake of CO2")

```

```{r}
library(ggplot2)
ggplot(CO2, aes(x= Type, y= uptake, fill = Treatment)) + geom_violin() + xlab("City") + ylab("Uptake of CO2") + coord_flip()

```

```{r}
library(ggplot2)
ggplot(CO2, aes(x= Type, y= uptake, fill = Treatment)) + geom_violin(trim = FALSE) + xlab("City") + ylab("Uptake of CO2")

```

