---
title: "Lecture 3.7 Notebook"
author: "Lindsay Waldrop"
date: "10/25/2021"
output: html_notebook
---


## 3.7 Debugging

Debugging is the process of removing errors in code that cause it to malfunction. This can include removing error messages or unintended/unexpected behavior or results. Problem solving these issues is a skill that requires practice and a solid understanding of what is happening within your script and function. 

__Four General Strategies of Debugging:__ 

 i. Check for the most common (i.e. “screaming toddler”) problems.
 ii. Figure out where the error is.
 iii. Google the error.
 iv. Create a hypothesis and test it.

### I. R's Screaming Toddler Problems

R will give you error messages that don’t make sense and don’t seem connected to the problem. It’s like a toddler: it can tell you things, but those things aren’t always useful to solving the problem at hand.

Try these common problems first: 

#### 1. It can’t find the object/function.

Errors look like: 
```{r, include=TRUE}
jake
```

```{r, include=TRUE}
a <- function() 3
a[1]
```

```{r, include=TRUE}
read.csv("data.csv")
```

```{r, include=TRUE}
ggplot()
```

Try these things to fix it: 

 * Check spelling
 * Check capitalization/case
 * Check the working directory/location of the file
 * Check to make sure object is in your “local” environment (is the package loaded? is your function including the right inputs?)
 
#### 2. It’s using an unexpected value.

Errors look like: 
```{r, include=TRUE}
a[,1]
```

```{r, include=TRUE}
b <- 1:10
b[,1]
```

```{r,include=TRUE}
mean(1,32,25,2)
```

Try these things to fix it: 

 * Is R calling the object you think it is? 
 * Clear your environment and try again. (Restart R)
 * Look closely at the arguments in a function, are you sure they are in the right order/the correct number?
 * Is the object the same size as what you’re calling?
 
#### 3. It wants a different data class.

Errors look like: 
```{r, include=TRUE}
a[,1]
```

```{r, include=TRUE}
b[,1]
```

```{r, include=TRUE}
sum("a")
```

```{r, include=TRUE}
C("sum","mean","average")
```

Try these things to fix it: 

 * Is what you are doing to the object appropriate? (specifically indexing)
 * Is that the data type that a function wants as an input?
 * Look closely at the arguments in a function, are you sure they are in the right order/the correct number?
 
### II. Figure Out Where the Error Is

If it’s not one of the most common problems, next step is to figure out where the error is and get more information about it. 

 * READ THE ERROR MESSAGE. Even if it’s not helpful, it will usually help you figure out what line the problem is at. 
 * Use `traceback()`, this can help by identifying the lines in each environment that are throwing errors.
 * Use the script editor to help point out any syntax errors. 
 * Trace back the error yourself by running a script line-by-line until you hit the error. 
 * If inside a function, manually assign arguments and then step through line-by-line. 
 
### III. Google it

The most helpful thing to do sometimes is to google an error message to see if someone else has already fixed it! 

To maximize search results for success, don’t include too much specific information about the error such as object names. Google the general parts of the error message: https://letmegooglethat.com/?q=object+of+type+%27closure%27+is+not+subsettable

Be sure to read the results carefully, read several entries (not just the first result), and try to understand the problem. 

### IV. Create a Hypothesis and Test It

After reading potential answers, form a hypothesis and figure out how to test it. This will depend on the particular problem, but will almost always involve simply trying different things until both of these things happen: 1) the error goes away, and 2) you understand the error. 

Try correcting the error with `a[,1]`:
```{r, include=TRUE}
a[,1]
```

What is your conclusion about this error?

### Practice Debugging a Function

Here is a function that doesn't work when you call it. Practice debugging this function so that it works correctly when called. 

```{r, include=TRUE}
my.function <- function(vec1,vec2){
  answers <- matrix(NA, nrow = 2, ncol = 5)
  row.names(answers)<- c("vec1","vec2")
  colnames(answers)<- c("sum", "rangelow","rangehigh","mean","sd")
  answers[1,1] <- sum(vec1)
  answers[2,1] <- sum(vec2)
  answers[1,2:3] <- range(vec1)
  answers[2,2:3] <- range(vec2)
  answers[1,4]<- mean(vec1)
  answers[2,4] <- mean(vec2)
  answers[1,5] <- sd(vec1)
  answers[2,5] <- sd(vec2)
  return(answers)
}

summary.answers <- my.function(1:10,c("1","10","15"))
```

Could you add a conditional to prevent this problem and give a "better" error message? Error messages can be set using `stop("Your message here")`.