---
title: "skill check 2.1.Rmd"
author: Rachelle, Azure, Camila, Brian
date: October 6, 2021
  output: html_document
---
```{r}
iris
```
download ggplot2 to access iris

```{r}
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, col=Species)) +
       geom_point(pch=0, size=2) +
  xlab("Sepal.Length") + ylab("Sepal.Width")
```
The point geom is used to create scatterplots. The scatterplot is most useful for displaying the relationship between two continuous variables. It can be used to compare one continuous and one categorical variable, or two categorical variables.

```{r}
data("iris")
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, col=Species)) +
  geom_point(pch=0, size=2) +
  geom_line() +
   xlab("Sepal.Length") + ylab("Sepal.Width")
```

```{r}
library(lattice)
data("iris")
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, col=Species)) +
  geom_line(pch=0, size=1) + 
  xlab("Sepal.Length") + ylab("Sepal.Width")
```
geom_line() makes line plots, which connects the points found in the ggplot above. 

```{r}
data("iris")
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, col=Species)) +
  geom_qq_line(aes(sample=Sepal.Width), pch=0, size=1) + 
  xlab("Sepal.Length") + ylab("Sepal.Width")
```

```{r}
data("iris")
ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width, col=Species)) +
  geom_point(pch=0, size=2) + 
  geom_line() +
  geom_qq_line(aes(sample=Sepal.Width), pch=0, size=1) + 
  xlab("Sepal.Length") + ylab("Sepal.Width")
```
geom_qq_line() makes quantile-quantile plots. This helps you compare multiple probability distributions.